An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2022-06-29 poly-embed-journal/poly-embed-journal.tex
meeting edits

\begin{claim}\label{claim:extended-poly-risk-poly}
	For any minimizable function $L$ such that $\risk L$ is polyhedral, its extension $\risk L_+$ is also polyhedral.
\end{claim}
\begin{proof}
  We will think of $\risk L$ as defined $\risk L:\reals^\Y\to\reals_+\cup\{-\infty\}$  with $\dom(\risk L) = \simplex$.
For $p \in \simplex$, we know $\sum_i p_i = 1$, and can write any inner product $\inprod{p}{b} - \beta = \inprod{p}{b} - \inprod{p}{\beta \ones} = \inprod{p}{b - \beta \ones}$.
If $p \not \in \simplex$, then $\risk L(p) = -\infty$.
Moreover, since $\risk L$ is polyhedral, it is finitely generated \citep[Proposition 19.1.2]{rockafellar1997convex} and can be written
\newcommand{\B}{\mathcal{B}} 
\begin{align*}
\risk L(p) 
&= \min(\inprod{p}{b_1} - \beta_1, \ldots, \inprod{p}{b_k} - \beta_k) - \delta(p \mid \simplex)\\
&= \min(\inprod{p}{b_1 - \beta_1 \ones}, \ldots, \inprod{p}{b_k - \beta_k \ones}) - \delta(p \mid \simplex)\\
&= \min_{(b, \beta) \in \B} \inprod{p}{b - \ones \beta} - \delta(p \mid \simplex)~,
\end{align*}
where $\B = \{(b_i, \beta_i)\}_{i = 1}^k$ from the second line.
For any $x \in \reals^\Y_+$, consider its normalization $\bar x$ with $(\bar x)_i = \frac{x_i}{\|x\|_1}$ such that $\bar x \in \simplex$.
As $\risk L_+$ is $1$-homogeneous, we observe $\risk L(x)_+ = \risk L_+(\|x\|_1 \bar x) = \|x\|_1 \risk L_+(\bar x) = \|x\|_1 \risk L(\bar x) \|x\|_1 = \min_{(b, \beta) \in \B} \inprod{\bar x}{b - \ones \beta}$ for all $x \in \reals^\Y_+$, which is polyhedral as the pointwise min over a finite set of linear functions. 
\raft{Error in the conversion to $\risk L_+$: I think you need to multiply by $\|x\|_1$.  But maybe an easier route is to simply replace the $\delta(p \mid \simplex)$ with $\delta(x \mid \reals^\Y_+)$ and observe that (a) the result is 1-homogenous, and (b) agrees with $\risk L$ on $\simplex$, ergo, must be its 1-homog extension.}
\end{proof}

>>>>

\begin{claim}\label{claim:extended-poly-risk-poly}
	For any minimizable function $L$ such that $\risk L$ is polyhedral, its extension $\risk L_+$ is also polyhedral.
\end{claim}
\begin{proof}
  We will think of $\risk L$ as defined $\risk L:\reals^\Y\to\reals_+\cup\{-\infty\}$  with $\dom(\risk L) = \simplex$.
For $p \in \simplex$, we know $\sum_i p_i = 1$, and can write any inner product $\inprod{p}{b} - \beta = \inprod{p}{b} - \inprod{p}{\beta \ones} = \inprod{p}{b - \beta \ones}$.
If $p \not \in \simplex$, then $\risk L(p) = -\infty$.
Moreover, since $\risk L$ is polyhedral, it is finitely generated \citep[Proposition 19.1.2]{rockafellar1997convex} and can be written
\newcommand{\B}{\mathcal{B}} 
\begin{align*}
\risk L(p) 
&= \min(\inprod{p}{b_1} - \beta_1, \ldots, \inprod{p}{b_k} - \beta_k) - \delta(p \mid \simplex)\\
&= \min(\inprod{p}{b_1 - \beta_1 \ones}, \ldots, \inprod{p}{b_k - \beta_k \ones}) - \delta(p \mid \simplex)\\
&= \min_{(b, \beta) \in \B} \inprod{p}{b - \ones \beta} - \delta(p \mid \simplex)~,
\end{align*}
where $\B = \{(b_i, \beta_i)\}_{i = 1}^k$ from the second line.
We claim that $\risk L_+(x) = \min_{(b, \beta) \in \B} \inprod{x}{b - \ones \beta} - \delta(x \mid \reals^\Y_+)$, as this form is clearly 1-homogenous and agrees with $\risk L$ on $\simplex$.
As $\B$ is a finite set, $\risk L_+$ is polyhedral.
% For any $x \in \reals^\Y_+$, consider its normalization $\bar x$ with $(\bar x)_i = \frac{x_i}{\|x\|_1}$ such that $\bar x \in \simplex$.
% As $\risk L_+$ is $1$-homogeneous, we observe $\risk L(x)_+ = \risk L_+(\|x\|_1 \bar x) = \|x\|_1 \risk L_+(\bar x) = \|x\|_1 \risk L(\bar x) \|x\|_1 = \min_{(b, \beta) \in \B} \inprod{\bar x}{b - \ones \beta}$ for all $x \in \reals^\Y_+$, which is polyhedral as the pointwise min over a finite set of linear functions. 
% \raft{Error in the conversion to $\risk L_+$: I think you need to multiply by $\|x\|_1$.  But maybe an easier route is to simply replace the $\delta(p \mid \simplex)$ with $\delta(x \mid \reals^\Y_+)$ and observe that (a) the result is 1-homogenous, and (b) agrees with $\risk L$ on $\simplex$, ergo, must be its 1-homog extension.}
\end{proof}
